Toggle Smell Detection in Google Chrome

### 2015-12-08 paper/paper.tex
Change some keyword and correct spelling

\begin{abstract}
Identifying code smell is the first step to re-factor a software system. 
In Google Chrome developers use feature toggles to control their features 
and keep developing on a single trunk. This paper investigates code smell 
caused by improper use of feature toggles in Google Chrome that we call 
as toggle smell. Using feature toggles to hide/unhide features is an old 
concept but recently being practised in many software companies. Improper 
use of toggles might cause code smell including duplicate code, dead code, 
coupling and lack of cohesion. We classified the smells caused by toggles 
in six different patterns Dead Toggles, Nested Toggles, Combinatorial (spaghetti) Toggles, 
Mix of Compile-Time and Runtime Toggles, Legacy toggles and Spread Toggles. 
We created a tool ``Toggle Smell Detector (TSD)'' as an Eclipse plug-in using Eclipse C++ Development Tooling (CDT) to identify these toggle 
smells in major modules of Google Chrome source code. We found TODO 
nested toggles smells, TODO spaghetti toggles and TODO spread toggles in ``chrome'' and ``base'' modules of Google Chrome.\\
\end{abstract}

>>>>

\begin{abstract}
Identifying code smell is the first step to re-factor a software system. 
In Google Chrome developers use feature toggles to control their features 
and keep developing on a single trunk. This paper investigates code smell 
caused by improper use of feature toggles in Google Chrome that we call 
as toggle smell. Using feature toggles to hide/show features is an old 
concept but recently being practice in many software companies. Improper 
use of toggles might cause code smell including duplicate code, dead code, 
coupling and lack of cohesion. We classified the smells caused by toggles 
in six different patterns Dead Toggles, Nested Toggles, Combinatorial (spaghetti) Toggles, 
Mix of Compile-Time and Runtime Toggles, Legacy/Stable toggles and Spread Toggles. 
We created a tool ``Toggle Smell Detector (TSD)'' as an Eclipse plug-in using Eclipse C++ Development Tooling (CDT) to identify these toggle 
smells in major modules of Google Chrome source code. We found TODO 
nested toggles smells, TODO spaghetti toggles and TODO spread toggles in ``chrome'' and ``base'' modules of Google Chrome.\\
\end{abstract}
